---
title: "Mutual fund performance"
subtitle: "An emperical decomposition into stock-picking<br/>talent, style, transaction costs, and expenses"  
author: 
  - "Russ Wermers"
date: 'Journal of Finance, 2000'
output:
  xaringan::moon_reader:
    includes:
      after_body: insert-logo.html
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#A60F2D",
  secondary_color = "#4D4D4D",
  inverse_header_color = "#FFFFFF",
  # fonts
  header_font_google = google_font("Martel"),
  text_font_google = google_font("Lato"),
  code_font_google = google_font("Fira Mono")
)
```

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r xaringan-scribble, echo=FALSE}
xaringanExtra::use_scribble()
```


# Agenda

### Motivation

### Database

### Performance-Decomposition Methodology

### Emperical Findings

### Conclusion

---

class: inverse center middle, hide-logo

# Motivation

---
layout: true

## Motivation

---

### Why

#### For Me


- A year of mutual fund research
- An interest in regulation and compliance

_Risk Shifting and Mutual Fund Performance (Huang, Sialm, and Zhang - 2009)_

--

#### For Wermers

> "Do mutual fund managers who actively trade stocks add value?" 


> "These studies (Gruber, 1996 and Carhart, 1997) do not provide a promising picture of active mutual fund management-instead, the studies conclude that investors are better off, on average, buying a low-expense index fund. Yet, investors continue to pour money into actively managed funds in pursuit of performance." 


---

### What

> "In this paper, we employ a new database that allows a comprehensive look at the performance of the mutual fund industry at both the stock holdings level and the net returns level.  **With this database, we empirically decompose performance into several components to analyze the value of active fund management.**"

--


---
layout: false
class: inverse center middle, hide-logo

# Database

---
layout: false

## Database

.panelset[

.panel[.panel-name[CDA]
#### CDA Investment Technologies

]
.panel[.panel-name[CRSP]
#### CRSP NYSE/AMEX/Nasdaq
]
.panel[.panel-name[Diversification]
]
.panel[.panel-name[Summary Statistics]
]
]

---


class: inverse center middle, hide-logo

# Performance-Decomposition Methodology

---


class: inverse center middle, hide-logo

# Emperical Findings


---


class: inverse center middle, hide-logo

# Conclusion

---

.panelset[

.panel[.panel-name[Datetime]

]
.panel[.panel-name[Leverage]
#### Leverage is used to define the risk exposure of firms before and after the crisis.
]
.panel[.panel-name[Methodology]
]
.panel[.panel-name[Bailouts]
]
]


---

# Left-Column Headings

.left-column[
## First

## Second

## Third
]

.right-column[
Dolor quis aptent mus a dictum ultricies egestas.

Amet egestas neque tempor fermentum proin massa!

Dolor elementum fermentum pharetra lectus arcu pulvinar.
]

---
layout: true

## Blocks

---

### Blockquote

> This is a blockquote following a header.
>
> When something is important enough, you do it even if the odds are not in your favor.


---

.pull-left[
#### Here is an unordered list:

*   Item foo
*   Item bar
*   Item baz
*   Item zip
]

.pull-right[

#### And an ordered list:

1.  Item one
1.  Item two
1.  Item three
1.  Item four
]

---

### And a nested list:

- level 1 item
  - level 2 item
  - level 2 item
    - level 3 item
    - level 3 item
- level 1 item
  - level 2 item
  - level 2 item
  - level 2 item
- level 1 item
  - level 2 item
  - level 2 item
- level 1 item
]
