---
title: "FIN 596"
subtitle: "Week 4 Literature Review"  
author: 
  - ""
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    includes:
      after_body: insert-logo.html
    css: [default, xaringan-themer.css, my-theme.css]
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#A60F2D",
  secondary_color = "#4D4D4D",
  inverse_header_color = "#FFFFFF",
  # fonts
  header_font_google = google_font("Martel"),
  text_font_google = google_font("Lato"),
  code_font_google = google_font("Fira Mono")
)
```

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r xaringan-scribble, echo=FALSE}
xaringanExtra::use_scribble()
```

## Selection

.pull-left[
### Spring '22

- Cyber risk and the U.S. financial system: A pre-mortem analysis
- Common Risk Factors in Cryptocurrency
- Is Bitcoin Really Untethered?

### Summer '22 Literature

- Central Bank Digital Currency and Banks 
- Fuzzy-Trace Theory: Dual Processes in Memory, Reasoning, and Cognitive Neuroscience
- Artificial Intelligence in Finance
- Machine learning at central banks
]
.pull-right[
### Summer '22 Peer Reviewed 

- Availability, recency, and sophistication in the repurchasing behavior of retail investors
- Political Capital and Moral Hazard
- The customer knows best: The investment value of consumer opinions 
- Do Schocks to Personal Wealth Affect Risk-taking in Delegated Portfolios 
- Fire Sales and Impediments to Liquidity Provision in the Corporate Bond Market
- How Much Should We Trust Staggered Difference-in-Difference

### Interests & Future Research
]

---

class: inverse center middle, hide-logo

# Spring '22

---

layout: true

## Cyber risk and the U.S. financial system

---

### Methodology & Questions

---

### Data & Conclusions

---

layout: true

## Common Risk Factors in Cryptocurrency

---

### Methodology & Questions

---

### Data & Conclusions

---

layout: true

## Is Bitcoin Really Untethered?

---

### Methodology & Questions

---

### Data & Conclusions

---

layout: false

class: inverse center middle, hide-logo

# Summer '22 Peer Reviewed

---

layout: true

## Availability, recency, and sophistication in </br> the repurchasing behavior of retail investors

---

layout: true

## Political Capital and Moral Hazard

---

### Methodology & Questions

---

### Data & Conclusions

---

layout: true 

## The customer knows best: The investment value of consumer opinions 

---

layout: true 

## Do Schocks to Personal Wealth Affect Risk-taking in Delegated Portfolios 

---

### Methodology & Questions

---

### Data & Conclusions

---

layout: true 

## Fire Sales and Impediments to Liquidity Provision in the Corporate Bond Market

---

### Methodology & Questions

---

### Data & Conclusions

---

layout: true

## How Much Should We Trust Staggered Difference-in-Difference

---

### Methodology & Questions

---

### Data & Conclusions

---

class: inverse center middle, hide-logo

# Summer '22 Literature

---

layout: true

## Central Bank Digital Currency and Banks 

---

### Methodology & Questions

---

### Data & Conclusions

---

layout: true

## Fuzzy-Trace Theory: Dual Processes in Memory, Reasoning, and Cognitive Neuroscience

---

### Methodology & Questions

---

### Data & Conclusions

---

layout: true 

## Artificial Intelligence in Finance

---

### Methodology & Questions

---

### Data & Conclusions

---

layout: true 

## Machine learning at central banks

---

### Methodology & Questions

---

### Data & Conclusions

---

layout: false

class: inverse center middle, hide-logo

# Interests and Future Research

---

## Interests and Future Research


Text can be **bold**, _italic_, ~~strikethrough~~, or `inline code`.

[Link to another slide](#colors).

### Lorem Ipsum

Dolor imperdiet nostra sapien scelerisque praesent curae metus facilisis dignissim tortor. 
Lacinia neque mollis nascetur neque urna velit bibendum. 
Himenaeos suspendisse leo varius mus risus sagittis aliquet venenatis duis nec.

- Dolor cubilia nostra nunc sodales

- Consectetur aliquet mauris blandit

- Ipsum dis nec porttitor urna sed

---